\documentclass[11pt,twoside]{IEEEtran}

%opening
\title{STREAM-AP: A Process to Systematize Architectural Patterns Choice Bases on NFR}
\author{Paper by Fabio Silva, Marcia Lucena, and Leonardo Lucena\\Reviewed by Ryan Darras}

\begin{document}

\maketitle

\section{Suggestion for acceptance}
Strongly Decline

\section{Summary}
The authors state that by having such a large gap between non-functional requirements and system architecture, you run into a problem where the architecture isn't built appropriately early so that developers have to go back in and modify it. When you go in to modify the underlying architecture of a project, it involves a bunch of time when it comes to refactoring and redesigning systems so this isn't a good thing. This paper provides a process to improve STREAM so that non-functional requirements and system architecture are more closely related. 


\section{Positive points}
The figures with a title on the left and a progression system are very useful and informative.


\section{Negative points}
So far, I have found our readings abstracts and introduction to suffice in terms of understanding the overall concept of the paper. This one, however, is different; I really don't understand what the whole goal of the paper is after reading the abstract and intro.

Some sentences are very poorly formatted and hard to read. I find myself having to back track here and then to try and figure out what they meant.

Sooooooo many acronyms. Acronyms are awesome and incredible useful but damn...

Hard to read. Not because of the content, but because of the way it is written.

Fig. 8 looks like it was drawn by hand. You have text overlapping shapes and no real organization.

\section{Potential future work}
The authors have a point when they discuss how getting bad requirements (including non-functional requirements) can lead to poor choices in the architecture of a system which results in it needing to be updated later. In my eyes, there are many different routes one can take this idea and go with it, not even including using STREAM.

\section{Personal Note}
I have yet to find a paper that I dislike more than this one. I literally just read it and I feel like I don't know anything. Hopefully the team that presents this can do a good job of filling me in!

\end{document}
